Universal Anonymous Signatures

### 2022-05-05 prism-backend/research/gsac/model-uas.tex
Making a pass.

\comment{\textbf{DISCLAIMER}: I've done a major rewriting of most
  properties. For now, please ignore the text until I have been able to sync
  it.}

We now define our model for Universal Anonymous Signatures. At a very high
level, it is a combination of the main models for group signatures and
anonymous credentials -- we try to extract the most useful features from both.
Instead of considering just one group, as in group signatures, we directly and
explicitly include support for multiple issuers as in anonymous credentials.
Moreover, instead of letting each user own a single credential, we allow
multiple credentials per user, even within the same group. This of course
makes us put forward refined notions of anonymity, traceability and
non-frameability. Note that, property-wise, we keep the three main properties
from group signatures, rather than sticking to the two usual properties of
anonymous credentials (anonymity and unforgeability). This is a consequence
of keeping the inspection capability from group signatures, which we consider
crucial in order to ensure some sort of accountability even in very adversarial
contexts where the issuer may be corrupt.
%
But, as stated in the introduction, we go beyond just combining anonymous
credentials and group signatures, and include support for arbitrary policies
during issuance, signing, and inspection. Consequently, our model needs to
capture the flexibility that these policies provide. In short, manipulations of
the issuance policy are only considered forgeries if the adversary manages to
create a valid signature using a credential that was obtained by dishonestly
manipulating the issuance policy (we discuss this further in the traceability
definition). Signing policies are taken into account both in the anonymity
property, where we need to restrict that both credentials used to produce the
challenge signatures always satisfy the policy, and in traceability.
\commentwho{Jesus}{Think a bit more about the following claim, and update if
  needed.}
We cannot give any assurance on the signing policies when the issuers are
corrupt, and thus they are not considered in the non-frameability property.
Inspection policies are considered both in traceability and non-frameability,
where the adversary wins if it manages to somehow alter the correct output of
\Inspect. What is even suprising, is that given the possible non-injectivity of
the inspection function lets us reach an even stronger notion of anonymity.
Namely, \uline{we can allow the adversary to open challenge signatures, as
  long as the inspection function outputs the same value for both}. We give more
details on these aspects in the actual definitions of the security properties.
%
Finally, from a functional perspective, we require that both issuer and
inspector fix the issuance predicate \fissue and inspection function \finsp when
generating their public keys. Indeed, both will be part of the common group key.
This also makes our definitions easier, as supporting multiple issuance
predicate and inspection functions per group would require to consider many
special cases -- and, anyway, that would probably end up being equivalent to
just requiring that a new group needs to be created per each $(\fissue,\finsp)$
pair. On the other hand, signing policies can be defined at signing time (in
practice, most probably by the verifiers). This is in line with the usual
practice in anonymous credentials, that let users prove arbitrary claims on
their credentials, as long as they are met by the contained attributes.

\subsubsection{Syntax}
\label{sssec:syntax}

An \UAS scheme is composed by the following algorithms.

\todo{The notation for multisets is not strictly correct. Still, leaving it as
  is for now.}

\begin{description}
\item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all the other functions, even if not explicitly listed in their
  input parameters.
\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] Given global system
  parameters \parm, and the function \fissue to be used to check that credential
  requestors meet the conditions to be issued a credential, an issuer runs
  \IKeyGen to generate its issuing key pair. 
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.] Given global system
  parameters \parm, and function \finsp, an inspector runs \OKeyGen to generate
  its inspecting key pair. The function \finsp defines the type of utility that
  will be extractable from those pairs that do not meet conditions defined
  at signing time (typically, by verifiers).
\item[$\usk \gets \UKeyGen(\parm)$.] Given global system parameters
  \parm, returns a user's secret key.
\item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle
  \Obtain(\usk,\lbrace (\cred_i,\ipk_i)\rbrace_{i \in \Issuers},\attrs),
  \Issue(\isk,\lbrace \ipk_i \rbrace_{i \in \Issuers},\attrs))
  \rangle$.] %
  This interactive protocol lets a user with key \usk running the
  \Obtain process, receive a credential \cred from an issuer in the system, on
  attribute set $\attrs$. The user leverages a set of $(\cred_i,\ipk_i)$ pairs,
  where $\cred_i$ is a credential obtained from the issuer with public
  key $\ipk_i$. The user outputs the produced credential \cred, while
  the issuer outputs the protocol transcript \utrans for the produced
  credential. To ease notation, we assume that the group to which each
  credential belongs is available from the credential itself, and therefore
  omit the $\ipk_i$ values from the syntax, unless necessary to avoid ambiguity.
\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\lbrace (\cred_i,\ipk_i)
  \rbrace_{i \in \Issuers},\msg,\feval)$.] %
  Upon receiving a user secret key \usk, inspector public key \opk, a set of
  credential-issuer pairs $(\cred_i,\ipk_i)$, a message \msg and evaluation
  function \feval, returns signature \sig and value \yeval.
\item[$1/0 \gets \Verify(\opk, \lbrace \ipk_i \rbrace_{i \in \Issuers},\sig,
  \yeval,\msg,\feval)$.] Checks whether $(\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys $\ipk_i$, for evaluation function \feval and inspector key \opk.
\item[$(\yinsp,\iproof)/\bot \gets \Inspect(\osk,\lbrace \ipk_i
  \rbrace_{i \in \Issuers},\sig,\yeval,\msg,\feval)$.] %
  Executed by the inspector with private key \osk. Receives a signature $(\sig,
  \yeval)$ over message \msg and evaluation function \feval, generated using
  credentials issued by the issuers with public keys $\ipk_i$. If \sig is valid,
  the function outputs a value $\yinsp$ derived from the signer's public key,
  credentials, message, and signature, as well as a proof of correct
  inspection.
\item[$1/0 \gets \Judge(\opk,\lbrace ipk_i \rbrace_{i \in \Issuers},\yinsp,
  \iproof,\sig,\yeval,\msg,\feval)$.] %
  Checks if \iproof is a valid inspection correctness proof for the value \yinsp,
  obtained by applying \Inspect to the the signature $(\sig,\yeval)$ over
  message \msg, and for evaluation function \feval. 
\end{description}

\paragraph{Issuance, evaluation, and inspection functions.} %
We emphasize that, both in our syntax definition, as well as on the following
modelling, we make use of three different and abstract functions: \fissue,
\feval and \finsp. The three functions are introduced to allow customized
governance of the resulting instantiation of an \UAS scheme. They will be
defined by different parties, but in all cases, they are run by users (maybe,
on user-private data). Also, in all cases, the user has to prove correctness of
their computation. We introduce them next, \todo{and will give concrete examples
  in \secref{sec:uac-instantiation}.}

\todo{Do our definitions protect from absurd schemes that leak \usk or \scred via
  \fissue or \feval (I guess \finsp is ok)? E.g., $\feval(\usk,\scred,\msg) =
  \usk$ deanonymizes the signer. I guess that anonymity should prevent that.
  But check.}

\begin{description}
\item[$\fissue: (\upk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},\attrs)
  \rightarrow 0/1$.] Chosen by issuers within a family of functions \famfissue,
  the issuance function defines what customized conditions an issuer requires
  in order to issue credentials, when receiving a request from user with public
  key \upk, for attributes \attrs. \fissue may run checks on a (possibly empty)
  set of additional credentials $\cred_i$, all bound to \upk, and possibly
  issued by other issuers. \fissue returns $1$ to accept a request, $0$ to
  reject it.
\item[$\feval: (\upk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},\msg)
  \rightarrow \yeval$.] Evaluation functions, from a family of functions
  \famfeval, can be set on a per-signature basis. The evaluation function
  defines customized conditions to be met by the owner of a user key \upk and
  credentials $\cred_i$, bound to \upk, in order to sign a concrete message
  \msg. Its outputs \yeval must belong in a well defined set \rngfeval.
\item[$\finsp: (\yeval,\upk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},
  \msg) \rightarrow \yinsp$.]
  Chosen by inspectors from a family of functions \famfinsp. The inspection
  functions define what utility value, derived from the user's public key,
  credentials, and signed message, should be extractable by an inspector.
  Note that \finsp also receives as input a value in the range of the \feval
  function, \rngfeval. This will allow inspection logic to depend on the value
  produced by the evaluation function. The output of \finsp is a value
  \yinsp, which must belong in a well defined set \rngfinsp.
\end{description}

We emphasize that, even though \finsp and \feval seem redundant, they are not.
To see this, observe that \finsp is defined by inspectors, and will be fixed in
all signatures ``inspectable'' by the inspector that defined it. On the other
hand, \feval can be defined by (e.g.) verifiers and, as such, it can be changed
on a per-signature basis, even if the signatures use the same \finsp. Thus,
\feval can (and is intended to) be programmed to contain the conditions set by
(e.g.) verifiers for signatures they receive; whereas \finsp can (and is intended
to) be programmed to extract specific utility values when needed, which may
depend on the checks required by the verifier a signature was intended to.

\paragraph{Helper functions \ExtractIssue and \ExtractSign.} In our modelling,
we assume the existence of three functions, \Identify, \ExtractIssue and
\ExtractSign. They are not functions available in the actual scheme, but rather
to the challenger, in the experiments we use to formalize security fof \UAS.
Indeed, similar techniques have been used before to prove security in
privacy-preserving schemes with some sort of accountability, but that do not
offer conventional opening as vanilla group signatures. For instance, see
related works on DAA \cite{bfg+11,cdl16} and group signature variants
\cite{dl21,fgl21,gl19,lnpy21}. More concretely, both functions are as follows:

\begin{description}
\item[$\Identify(\usk,\attrs_{\cred},\cred)$.] Returns $1$ if \cred has been
  issued over attributes $\attrs_{\cred}$ and for a user with secret key \usk.
  Otherwise, it returns $0$.
\item[$\ExtractIssue(\utrans) \rightarrow (\usk,\scred,\attrs_{\scred})$.]
  Receives an $\langle \Obtain, \Issue \rangle$ transcript, and returns the
  credentials (if any), their attributes, and the user secret key used during
  the execution of the $\langle\Obtain,\Issue\rangle$ protocol. It clearly needs
  an honest issuer as, otherwise, the transcripts won't be available.
  Consequently, we only use it to define the properties that require an honest
  issuer.
\item[$\ExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval) \rightarrow (\usk,\scred)$.]
  Receives a signature pair $(\sig,\yeval)$, as well as the inspector identifier
  \oid, and the identifiers of all issuers of the credentials used to produce the
  signature over \msg, and for \feval. It outputs the user secret key
  and credentials used to generate the signature.
\end{description}

Note that, both for the three functions, in the case of credentials,
transcripts, and signatures by honest users, it is enough to have access to the
corresponding state information (described below) maintained by the challenger
in our experiments. For credentials and join transcripts of corrupt users, or
dishonestly produced signatures, we do need to perform actual extraction. How to
do this will depend on each specific construction. Certainly, the challenger
needs special knowledge/power such as decryption trapdoors, the ability to
rewind the game, or program random oracles; the approach needs thus to depend on
the concrete construction. Although, for the case of \ExtractIssue, online
extractability (or alternative requirements, such as non-parallel or logarithmic
number of joins) is necessary. %
\todo{\needcite Paper from Camenisch and Shoup on the need
  for online extractability?} \todo{How do we do this in our construction(s)?
  Can we be more specific here? Also, this poses an interesting question: Is
  extraction a requirement for this kind of schemes? Can we find alternative
  definitions?}

\paragraph{Global Variables.} %
The environment manages several global variables in the games posed to the
adversary. Users are referred to with user identifiers, \uid; for credentials,
we use \cid; for groups, \gid. For credentials and groups, we use bold font to
denote sets: i.e., \scid and \sgid denote sets of credential and group
identifiers. All tables/sets are initialized as empty tables/sets, denoted
with $\emptyset$.

\begin{description}
\item[Tables for parties]:
  \begin{description}
  \item[\HU and \CU.] Keep track of honest (\HU) and corrupted (\CU) users;
    i.e., they are sets of {\uid}s.
  \item[\HI and \CI.] Keep track of honest (\HI) and corrupted (\CI) issuers;
    i.e., they are sets of {\iid}s.
  \item[\HO and \CO.] Keep track of honest (\HO) and corrupted (\CO) inspectors;
    i.e., they are sets of {\oid}s.
  \end{description}
\item[Tables for keys]:
  \begin{description}
  \item[\UK.] \UK maintains user keys $\usk$. To refer to the key of a specific
    user, we use $\UK[\uid]$. 
  \item[\IK, \PUBIK and \PRVIK.] \IK maintains issuer key pairs, where
    $\IK[\iid]$ refers to the key pair of the issuer with identifier \iid. We
    use \PUBIK to refer to the public component, which also includes the \fissue
    function; and \PRVIK refers to the private component of the key pair.
  \item[\OK, \PUBOK, \PRVOK.] Same as \IK, but for inspector key pairs. Instead
    of \fissue, \OK includes the \finsp function.
  \end{description}
\item[Tables for credentials-related data]:
  \begin{description}
  \item[\CRED.] Stores information related to credentials obtained by users in
    the system. Thus, it is indexable by \cid. More specifically, it stores
    tuples of the form $(\uid,\cred,\iid,\attrs,\scid)$, where \uid is the
    identity of the owner of the credential, \cred (when available) is the
    credential itself, \iid is the identifier of the credential issuer, \attrs
    are the attributes included in \cred, and \scid are the identifiers of the
    credentials (if any) that \uid used to request \cred. For notational
    convenience, we may use $\CRED[\scid]$ to refer to $\CRED[\cid]$ for all
    $\cid \in \scid$. Also, when clear from context, we sometimes use
    $\CRED[\cid]$ (resp. $\CRED[\scid]$ to mean \cred (resp. \scred) in
    $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,\cdot)$ (resp. $\CRED[\scid]$).
  \item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
    ``\uid such that $\CRED[\cid] = (\uid, \cdot, \cdot, \cdot, \cdot)$''.
  \item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
    ``\attrs such that $\CRED[\cid] = (\cdot, \cdot, \cdot, \attrs, \cdot)$''.
  \item[\ISR.] For notational convenience, when we write $\ISR[\cid]$ we mean
    ``\iid such that $\CRED[\cid] = (\cdot, \iid, \cdot, \cdot, \cdot)$''.
  \end{description}
\item[Tables for signatures]:
  \begin{description}
  \item[\SIG.] Maintains signatures generated via the \SIGN oracle, on behalf
    of honest users. Entries of this table are $(\oid,\scid,\sig,\yeval,\msg,
    \feval)$, where \oid is the inspector chosen for the signature, \scid is the
    set of credentials used for signing, \feval is the evaluation function, and
    \sig and \msg are the produced signature and signed message.
  \item[\CSIG.] Maintains challenge signatures output to the adversary; i.e.,
    the table is indexable by challenge signatures \csig.
    Each entry contains also $\cuid_b$ and $\scid_b$ the challenge user and
    credential identifiers set used to produce \csig; as well as the
    corresponding challenge user and credential set indexed by the complementary
    $1-b$; the signed message \msg and evaluation function \feval, the result of
    \feval, \yeval, and the inspector identifier \oid.
  \end{description}
\end{description}

@@

\begin{description}
\item[\IGEN.] Adds a new issuer to the game, generating its keypair and setting
  the associated issuance function.
\item[\OGEN.] Adds a new inspector to the game, generating its key pair and
  setting the associated evaluation and inspection functions.
\item[\ICORR.] Corrupts an existing (and honest) issuer, by giving its secret
  key to the adversary.
\item[\OCORR.] Corrupts an existing (and honest) inspector, by giving its secret
  key to the adversary.  
\item[\HUGEN.] Adds a new honest user to the game, by honestly generating
  the user's key pair.
\item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
  user already exists and is honest, corrupts it.
\item[\RREG.] Reads the given transcript table entry.
\item[\WREG.] Sets a transcript table entry to the given value.
\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
  the game, on behalf of an honest user.
\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer
  in games that support it, by letting it interact with honest users who want to
  receive credentials.
\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
  requesting an honest issuer to produce credentials for them.
\item[\SIGN.] Lets the adversary get signatures from credentials belonging
  to honest users.
\item[\OPEN.] Given an honestly produced signature, lets the adversary learn
  which credential was used to produce it.
\item[\CHALb.] Upon receiving two challenge credentials, a common intersecting
  set of attributes, and a message, returns a signature produced by one of these
  two credentials, defined by the bit $b$, which is established in the anonymity
  game.
\end{description}

@@

        \procedure{$\INSPECT(\oid,\sig,\yeval,\msg)$}{%
          \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\sig,\yeval,\msg,\feval)
          \in \SIG[\uid] \\
          (\yinsp,\iproof) \gets
          \Inspect(\PRVOK[\oid],\GK[\scid],\sig,\yeval,\msg,\feval) \\
          \pcif \CSIG[\sig] \neq \bot: \\
          \pcind \textrm{Parse $\CSIG[\sig]$ as $(\oid,\cuid_b,\scid_b,\msg,
            \feval,\yeval$} \\
          \hspace*{83pt}\cuid_{1-b},\csig_{1-b},\scid_{1-b}) \\
          \pcind (\yinsp',\iproof') \gets
          \Inspect(\PRVOK[\oid],\IK[\siid],\\
          \hspace*{107pt} \sig_{1-b},\msg,\feval) \\
          \pcind \pcif \yinsp' \neq \yinsp: \pcreturn \bot \\
          \pcreturn (\yinsp,\iproof)
        }

@@

\paragraph{Correctness.} %
Correctness of \UAS schemes is formalized through the experiment in
\figref{fig:exp-uas-corr}. It states that a signature over any arbitrary message
and valid function \feval produced honestly leveraging credential set \scid,
owned by user \uid, is accepted by \Verify. Moreover, all the credentials in
\scid met the conditions set by the corresponding \fissue defined by the issuer
which issued each credential. Similarly, the output \yeval of \feval matches the
value produced by \Sign alognside with \sig; and the value produced by \Inspect
is accepted by \Judge, and matches the output of applying \finsp on \yeval, the
credentials, user key, and message.

>>>>

We now define our model for Universal Anonymous Signatures. Property-wise, we
maintain anonymity, non-frameability, and include two extra unforgeability
properties: unforgeability of issuance, which ensures that issuance policies
are not circumvented; and unforgeability of signatures, guaranteeing that
signing policies are respected, as well as soundness of opening.

From a functional perspective, we require that each issuer and opener fix
the issuance predicate \fissue and opener function \finsp when generating
their public keys. On the other hand, signature evaluation functions \feval can
be defined at signing time. This is in line with the usual practice in anonymous
credentials, that let
users prove arbitrary claims on their credentials, as long as they are met by
the contained attributes. In practice, most probably, the signing policy to be
employed in each signature will be defined by the verifier (or jointly between
user and verifier), including the specification of which inspector will be
able to post-process signatures\footnote{See, for instance, the concept of
  presentation exchanges, or requests, in the context of Verifiable Credentials:
  \url{https://identity.foundation/presentation-exchange/} (last access, May
  5th, 2022).}. Beyond these general policies, which already give much
flexibility, the syntax for \UAS supports multiple issuers and openers, and
lets users leverage multiple credentials to request issuance of new ones, and
to produce signatures.

\subsubsection{Syntax.} An \UAS scheme is composed by the following algorithms:

\begin{description}
\item[$\parm \gets \Setup(\secpar)$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all the other functions, even if not explicitly listed in their
  input parameters.
\item[$(\ipk,\isk) \gets \IKeyGen(\parm,\fissue)$.] Given global system
  parameters \parm, and the function \fissue to be used to check that credential
  requestors meet the conditions to be issued a credential, an issuer runs
  \IKeyGen to generate its issuing key pair. 
\item[$(\opk,\osk) \gets \OKeyGen(\parm,\finsp)$.] Given global system
  parameters \parm, and function \finsp, an opener runs \OKeyGen to generate
  its opening key pair. The function \finsp defines the type of utility that
  will be extractable from signatures.
\item[$\usk \gets \UKeyGen(\parm)$.] Given global system parameters
  \parm, returns a user's secret key.
\item[$\langle \cred/\bot,\utrans/\bot \rangle \gets
  \langle
  \Obtain(\usk,\lbrace (\cred_i,\ipk_i)\rbrace_{i \in \Issuers},\attrs),
  \Issue(\isk,\lbrace \ipk_i \rbrace_{i \in \Issuers},\attrs))
  \rangle$.] %
  This interactive protocol lets a user with key \usk running the
  \Obtain process, receive a credential \cred from an issuer in the system, on
  attribute set $\attrs$. The user leverages a set of $(\cred_i,\ipk_i)$ pairs,
  where $\cred_i$ is a credential obtained from the issuer with public
  key $\ipk_i$. The user outputs the produced credential \cred, while
  the issuer outputs the protocol transcript \utrans for the produced
  credential. To ease notation, we assume that the issuer public key associated
  to credential is available from the credential itself, and therefore
  omit the $\ipk_i$ values from the syntax, unless necessary to avoid
  ambiguity.
\item[$(\sig,\yeval) \gets \Sign(\usk,\opk,\lbrace (\cred_i,\ipk_i)
  \rbrace_{i \in \Issuers},\msg,\feval)$.] %
  Upon receiving a user secret key \usk, opener public key \opk, a set of
  credential-issuer pairs $(\cred_i,\ipk_i)$, a message \msg and evaluation
  function \feval, returns signature \sig and value \yeval.
\item[$1/0 \gets \Verify(\opk, \lbrace \ipk_i \rbrace_{i \in \Issuers},\sig,
  \yeval,\msg,\feval)$.] Checks whether $(\sig,\yeval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys $\ipk_i$, for evaluation function \feval and inspector key \opk.
\item[$(\yinsp,\iproof)/\bot \gets \Open(\osk,\lbrace \ipk_i
  \rbrace_{i \in \Issuers},\sig,\yeval,\msg,\feval)$.] %
  Executed by the opener with private key \osk. Receives a signature $(\sig,
  \yeval)$ over message \msg and evaluation function \feval, generated using
  credentials issued by the issuers with public keys $\ipk_i$. If \sig is valid,
  the function outputs a value $\yinsp$.
\item[$1/0 \gets \Judge(\opk,\lbrace ipk_i \rbrace_{i \in \Issuers},\yinsp,
  \iproof,\sig,\yeval,\msg,\feval)$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $(\sig,\yeval)$ over
  message \msg, and for evaluation function \feval. 
\end{description}

\paragraph{Issuance, evaluation, and opening functions.} %
We emphasize that, both in our syntax definition, as well as on the following
modelling, we make use of three different and abstract functions: \fissue,
\feval and \finsp. The three functions are introduced to allow customized
governance of the resulting instantiation of an \UAS scheme. They will be
defined by different parties, but in all cases, they are run by users (maybe,
on user-private data). Also, in all cases, the user has to prove correctness of
their computation. We introduce them next, \todo{and will give concrete examples
  in \secref{sec:uas-instantiation}.}

\begin{description}
\item[$\fissue: (\usk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},\attrs)
  \rightarrow 0/1$.] Chosen by issuers within a family of functions \famfissue,
  the issuance function defines what customized conditions an issuer requires
  in order to issue credentials, when receiving a request from user with secret
  key \usk, for attributes \attrs. \fissue may run checks on a (possibly empty)
  set of additional credentials $\cred_i$, all bound to \usk, and possibly
  issued by other issuers. \fissue returns $1$ to accept a request, $0$ to
  reject it.
\item[$\feval: (\usk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},\msg)
  \rightarrow \yeval$.] Signing evaluation functions, from a family of functions
  \famfeval, can be set on a per-signature basis. They receive the user secret
  key \usk, credentials $\cred_i$, and message to be signed \msg, and can be
  used to control the information related to the signer that will be revealed
  alongside a signature, and to modulate the behaviour of \finsp. Its outputs
  \yeval must belong in a well defined set \rngfeval.
\item[$\finsp: (\yeval,\usk,\lbrace (\cred_i,\ipk_i) \rbrace_{i \in \Issuers},
  \msg) \rightarrow \yinsp$.]
  Chosen by openers from a family of functions \famfinsp. The opening
  functions define what utility value, derived from the user's secret key,
  credentials, and signed message, should be extractable by an opener.
  Note that \finsp also receives as input a value in the range of the \feval
  function, \rngfeval. This allows opening logic to depend on the value
  produced by the evaluation function. The output of \finsp is a value
  \yinsp, which must belong in a well defined set \rngfinsp.
\end{description}

We emphasize that, even though \finsp and \feval seem redundant, they are not.
To see this, observe that \finsp is defined by inspectors, and will be fixed in
all signatures that can be opened by the opener who defined it. On the other
hand, \feval can be defined by (e.g.) verifiers on a per-signature basis, even
if the signatures use the same \finsp. Thus, \feval can be programmed to contain
the conditions set by (e.g.) verifiers for signatures they receive; whereas
\finsp can be programmed to extract specific utility values when needed, which
may depend on the checks required by the verifier a signature was intended to.

\paragraph{Helper functions \Identify, \ExtractIssue and \ExtractSign.} In our
modelling, we assume the existence of three functions, \Identify, \ExtractIssue
and \ExtractSign. They are not functions available in the actual scheme, but
rather to the challenger in the experiments we use to formalize security fof
\UAS. Indeed, similar techniques have been used before to prove security in
privacy-preserving schemes with some sort of accountability, but that do not
offer conventional opening as vanilla group signatures. For instance, see
related works on DAA \cite{bfg+11,cdl16} and group signature variants
\cite{dl21,fgl21,gl19,lnpy21}. More concretely, both functions are as follows:

\begin{description}
\item[$\Identify(\usk,\attrs_{\cred},\cred)$.] Returns $1$ if \cred has been
  issued over attributes $\attrs_{\cred}$ and for a user with secret key \usk.
  Otherwise, it returns $0$. In order to be meaningful, this requires that,
  for every $(\attrs_{\cred},\cred)$ pair, there is at most one \usk that makes
  \Identify return $1$.
\item[$\ExtractIssue(\utrans) \rightarrow (\usk,\scred,\attrs_{\scred})$.]
  Receives an $\langle \Obtain, \Issue \rangle$ transcript, and returns the
  credentials (if any), their attributes, and the user secret key used during
  the execution of the $\langle\Obtain,\Issue\rangle$ protocol. It clearly needs
  an honest issuer as, otherwise, the transcripts won't be available.
  Consequently, we only use it to define the properties that require an honest
  issuer.
\item[$\ExtractSign(\oid,\siid,\sig,\yeval,\msg,\feval) \rightarrow (\usk,
  \scred)$.] Receives a signature pair $(\sig,\yeval)$, as well as the opener
  identifier \oid, and the identifiers of all issuers of the credentials used to
  produce the signature over \msg, and for \feval. It outputs the user secret
  key and credentials used to generate the signature.
\end{description}

Note that, for the three functions, in the case of credentials, transcripts,
and signatures by honest users, it is enough to have access to the corresponding
state information (described below) maintained by the challenger in our
experiments. For credentials and join transcripts of corrupt users, or
dishonestly produced signatures, we do need to perform actual extraction. How to
do this will depend on each specific construction. Certainly, the challenger
needs special knowledge/power such as decryption trapdoors, the ability to
rewind the game, or program random oracles. The approach needs thus to depend on
the concrete construction, although. Although, for the case of \ExtractIssue,
online extractability \needcite (or alternative requirements, such as
non-parallel or logarithmic number of joins) is necessary.

\paragraph{Global Variables.} %
The environment manages several global variables in the games posed to the
adversary. Users are referred to with user identifiers, \uid; for credentials,
we use \cid; for issuers, \iid; and for openers, \oid. In all cases, we use bold
font to denote sets: e.g., \scid and \siid denote sets of credential and issuer
identifiers. All tables/sets are initialized as empty tables/sets.

\begin{description}
\item[Tables for parties]:
  \begin{description}
  \item[\HU and \CU.] Keep track of honest (\HU) and corrupted (\CU) users;
    i.e., they are sets of {\uid}s.
  \item[\HI and \CI.] Keep track of honest (\HI) and corrupted (\CI) issuers;
    i.e., they are sets of {\iid}s.
  \item[\HO and \CO.] Keep track of honest (\HO) and corrupted (\CO) openers;
    i.e., they are sets of {\oid}s.
  \end{description}
\item[Tables for keys]:
  \begin{description}
  \item[\UK.] \UK maintains user keys $\usk$. To refer to the key of a specific
    user, we use $\UK[\uid]$. 
  \item[\IK, \PUBIK and \PRVIK.] \IK maintains issuer key pairs, where
    $\IK[\iid]$ refers to the key pair of the issuer with identifier \iid. We
    use \PUBIK to refer to the public component, which also includes the \fissue
    function; and \PRVIK refers to the private component of the key pair.
  \item[\OK, \PUBOK, \PRVOK.] Same as \IK, but for opener key pairs. Instead
    of \fissue, \OK includes the \finsp function.
  \end{description}
\item[Tables for credentials-related data]:
  \begin{description}
  \item[\CRED.] Stores information related to credentials obtained by users in
    the system. Thus, it is indexable by \cid. More specifically, it stores
    tuples of the form $(\uid,\cred,\iid,\attrs,\scid)$, where \uid is the
    identity of the owner of the credential, \cred (when available) is the
    credential itself, \iid is the identifier of the credential issuer, \attrs
    are the attributes included in \cred, and \scid are the identifiers of the
    credentials (if any) that \uid used to request \cred. For notational
    convenience, we may use $\CRED[\scid]$ to refer to $\CRED[\cid]$ for all
    $\cid \in \scid$. Also, when clear from context, we sometimes use
    $\CRED[\cid]$ (resp. $\CRED[\scid]$ to mean \cred (resp. \scred) in
    $\CRED[\cid] = (\cdot,\cred,\cdot,\cdot,\cdot)$ (resp. $\CRED[\scid]$).
  \item[\OWNR.] For notational convenience, when we write $\OWNR[\cid]$ we mean
    ``\uid such that $\CRED[\cid] = (\uid, \cdot, \cdot, \cdot, \cdot)$''.
  \item[\ATTR.] For notational convenience, when we write $\ATTR[\cid]$ we mean
    ``\attrs such that $\CRED[\cid] = (\cdot, \cdot, \cdot, \attrs, \cdot)$''.
  \item[\ISR.] For notational convenience, when we write $\ISR[\cid]$ we mean
    ``\iid such that $\CRED[\cid] = (\cdot, \iid, \cdot, \cdot, \cdot)$''.
  \end{description}
\item[Tables for signatures]:
  \begin{description}
  \item[\SIG.] Maintains signatures generated via the \SIGN oracle, on behalf
    of honest users. Entries of this table are $(\oid,\scid,\sig,\yeval,\msg,
    \feval)$, where \oid is the opener chosen for the signature, \scid is the
    set of credentials used for signing, \feval is the signing evaluation
    function, and \sig and \msg are the produced signature and signed message.
  \item[\CSIG.] Maintains challenge signatures output to the adversary; i.e.,
    the table is indexable by challenge signatures \csig.
    Each entry contains also $\cuid_b$ and $\scid_b$ the challenge user and
    credential identifiers set used to produce \csig; as well as the
    corresponding challenge user and credential set indexed by the complementary
    $1-b$; the signed message \msg and signing evaluation function \feval, the
    result of \feval, \yeval, and the opener identifier \oid.
  \end{description}
\end{description}

@@

\begin{description}
\item[\IGEN.] Adds a new issuer to the game, generating its keypair and setting
  the associated issuance function.
\item[\OGEN.] Adds a new inspector to the game, generating its key pair and
  setting the associated evaluation and inspection functions.
\item[\ICORR.] Corrupts an existing (and honest) issuer, by giving its secret
  key to the adversary.
\item[\OCORR.] Corrupts an existing (and honest) inspector, by giving its secret
  key to the adversary.  
\item[\HUGEN.] Adds a new honest user to the game, by honestly generating
  the user's key pair.
\item[\CUGEN.] Adds a new corrupt user to the game or, if the specified
  user already exists and is honest, corrupts it.
\item[\RREG.] Reads the given transcript table entry.
\item[\WREG.] Sets a transcript table entry to the given value.
\item[\OBTISS.] Lets the adversary add a new honestly generated credential to
  the game, on behalf of an honest user.
\item[\OBTAIN.] Enables the adversary to play the role of a dishonest issuer
  in games that support it, by letting it interact with honest users who want to
  receive credentials.
\item[\ISSUE.] Allows the adversary to play the role of dishonest users,
  requesting an honest issuer to produce credentials for them.
\item[\SIGN.] Lets the adversary get signatures from credentials belonging
  to honest users.
\item[\OPEN.] Given an honestly produced signature, outputs the result of the
  opening function, along with a correctness proof.
\item[\CHALb.] Upon receiving two challenge users and credential sets, a common
  singing evaluation function and a message, returns a signature produced by one
  of these two user and credential sets, defined by the bit $b$, which is
  established in the anonymity game.
\end{description}

@@

        \procedure{$\OPEN(\oid,\sig,\yeval,\msg)$}{%
          \textrm{Let}~\uid~\textrm{be s.t.}~(\oid,\scid,\sig,\yeval,\msg,\feval)
          \in \SIG[\uid] \\
          (\yinsp,\iproof) \gets
          \Inspect(\PRVOK[\oid],\GK[\scid],\sig,\yeval,\msg,\feval) \\
          \pcif \CSIG[\sig] \neq \bot: \\
          \pcind \textrm{Parse $\CSIG[\sig]$ as $(\oid,\cuid_b,\scid_b,\msg,
            \feval,\yeval$} \\
          \hspace*{83pt}\cuid_{1-b},\csig_{1-b},\scid_{1-b}) \\
          \pcind (\yinsp',\iproof') \gets
          \Inspect(\PRVOK[\oid],\IK[\siid],\\
          \hspace*{107pt} \sig_{1-b},\msg,\feval) \\
          \pcind \pcif \yinsp' \neq \yinsp: \pcreturn \bot \\
          \pcreturn (\yinsp,\iproof)
        }

@@

\paragraph{Correctness.} %
Correctness of \UAS schemes is formalized through the experiment in
\figref{fig:exp-uas-corr}. It states that a signature over any arbitrary message
and valid function \feval produced honestly leveraging credential set \scid,
owned by user \uid, is accepted by \Verify. Moreover, all the credentials in
\scid met the conditions set by the corresponding \fissue defined by the issuer
which issued each credential. Similarly, the output \yeval of \feval matches the
value produced by \Sign alongside with \sig; and the value produced by \Open
is accepted by \Judge, and matches the output of applying \finsp on \yeval, the
credentials, user key, and message.

\begin{definition}{(Correctness of \UAS)}
  \label{def:correctness-uas}
  An \UAS scheme is correct if, for any p.p.t. adversary $\adv$,
  $\ExpCorrect(1^\secpar)$ outputs 1 with negligible probability.
\end{definition}
